---
title: "ESM 206 Assignment 4"
author: "Grace Kumaishi"
date: "11/15/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(janitor)
library(here)
library(lubridate)
```

```{r}
# Read in data (HIDE THIS CODE CHUNK)
bonanza_hares <- read_csv(here("data", "bonanza_hares.csv")) %>%
  clean_names()
```


## Introduction

## Data and analyses

## Exploratory findings

### 1) Annual juvenile hare trap counts

```{r}
juv_hares <- bonanza_hares %>% 
  filter(age == "j") %>% 
  mutate(date_new = mdy(date)) %>%
  mutate(year_new = year(date_new)) %>% 
  count(year_new)

ggplot(data = juv_hares, aes(x = year_new, y = n)) +
  geom_line() +
  labs(x = "year", y = "count", title = "Number of juvenile hares trapped from 1999-2012") +
  theme_minimal() +
  scale_x_continuous(breaks = c(1999, 2001, 2003, 2005, 2007, 2009, 2011))
```


### 2) Visualize juvenile hare weights

Create a finalized data visualization (or visualizations) in which you compare **juvenile hare weights by sex and site (grid)** (ignore other variables). You should include groups where these variables are not recorded (`NA`). Include finalized figure captions below your visualization(s).

```{r}
juv_hares_sex_site <- bonanza_hares %>% 
  filter(age == "j") %>% 
  select("sex", "grid", "weight")

ggplot(data = juv_hares_sex_site, aes(x = weight)) +
  geom_density(aes(fill = sex, bins = 15, alpha = 0.8)) +
  facet_wrap(~grid + sex, nrow = 3) +
  theme_minimal()
```


### 3) Juvenile weight comparison (male & female snowshoe hares)

### 4) Relationship between juvenile weight & hind foot length

## Summary

## Citations 